Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-29 paper/ijcai16.tex
paper: singular.

A PC configurations is defined by eight attributes: computer type (laptop,
desktop, or tower), manufacturer (8 choices), CPU model (37), monitor size (8), RAM amount (10), storage (10)
size, and price.
%See Table~\ref{tab:pcdataset} for an overivew of the attributes.
The price attribute is defined as a linear combination of the other
attributes: this is a fair modeling choice, as often the price of a PC is
well approximated by the sum of the price of its components plus a bias due to
branding.
%
Interactions between attributes are expressed as Horn clauses (e.g. a certain manufacturer implies a set of possible CPUs).
% . An example
% constraint might look like this: ``if the manufacturer is Apple, then the
% CPU must be either a PowerPC G3 or a PowerPC G4''%
% %\footnote{Despite the components
% %included in the dataset, which are a bit outdated, the dataset itself is pretty
% %realistic.} \andrea{necessario?}
% , which can be encoded into MILP form as
% %
% $ (1 - x_\text{Apple}) + x_\text{G3} + x_\text{G4} \ge 1 $.
% %
% Note that only one of $x_\text{G3}$ and $x_\text{G4}$ can be 1 because
% of the mutual exclusivity constraints of the one-hot encoding.  
The
dataset includes 16 Horn constraints (the full list is omitted for
space limitations).
% constraints between the following attributes:
% manufacturer $\to$ type, manufacturer $\to$ CPU, type $\to$ RAM
% amount, type $\to$ storage size, type $\to$ monitor size, for 16 Horn
% constraints total. We do not report the full list due to space
% limitations. 
Note that the search space is of the order of hundreds of thousands of
candidate configurations, and is far beyond reach of existing Bayesian
approaches.

>>>>

A PC configuration is defined by eight attributes: computer type (laptop,
desktop, or tower), manufacturer (8 choices), CPU model (37), monitor size (8), RAM amount (10), storage (10)
size, and price.
%See Table~\ref{tab:pcdataset} for an overivew of the attributes.
The price attribute is defined as a linear combination of the other
attributes: this is a fair modeling choice, as often the price of a PC is
well approximated by the sum of the price of its components plus a bias due to
branding.
%
Interactions between attributes are expressed as Horn clauses (e.g. a certain manufacturer implies a set of possible CPUs).
% . An example
% constraint might look like this: ``if the manufacturer is Apple, then the
% CPU must be either a PowerPC G3 or a PowerPC G4''%
% %\footnote{Despite the components
% %included in the dataset, which are a bit outdated, the dataset itself is pretty
% %realistic.} \andrea{necessario?}
% , which can be encoded into MILP form as
% %
% $ (1 - x_\text{Apple}) + x_\text{G3} + x_\text{G4} \ge 1 $.
% %
% Note that only one of $x_\text{G3}$ and $x_\text{G4}$ can be 1 because
% of the mutual exclusivity constraints of the one-hot encoding.  
The
dataset includes 16 Horn constraints (the full list is omitted for
space limitations).
% constraints between the following attributes:
% manufacturer $\to$ type, manufacturer $\to$ CPU, type $\to$ RAM
% amount, type $\to$ storage size, type $\to$ monitor size, for 16 Horn
% constraints total. We do not report the full list due to space
% limitations. 
Note that the search space is of the order of hundreds of thousands of
candidate configurations, and is far beyond reach of existing Bayesian
approaches.
